se---
title: "R Notebook"
output: html_notebook
---

Sample info
```{r}
Samples <- read.table("SampleInfo.txt", header=T)
names <- as.data.frame(colnames(FRT))
Samples <- merge(names, Samples, by.x="colnames(FRT)", by.y="Sample", all.x = T)

write.table(Samples, "Samples.txt", col.names=T, row.names=F)
```

Gene length needed for edgeR
```{r}
length <- read.table("FRTlength.csv", sep=",", header=F, 
                 row.names = NULL, 
                 stringsAsFactors = FALSE)

length <- length[,c(3,5)]
length <- rownames.first(length)
colnames(length) <- c("length")

write.table(length, "length.txt", col.names=T, row.names=T )
```

Signal Annotation from Uniprot + Ecocarta and vesiclepedia
```{r}
#Downloaded fasta file of all genes with "signal" annotation from uniprot
#With excel isolated only the header, separated out the different parts of the header and kept only the part after GN= 
# remove any extra characters at the end
#Convert to flybase gene nemae with fly mine
#The whole list (6,431) after removing duplicates and anything lost in processing is 3279 genes

signal <- read.table("SignalDroso.FBgn.tsv", header=F, sep="\t")
signal <- subset(signal, signal$V4 == "Drosophila melanogaster")
signal <- signal[grep("FBgn", signal$V3),]
signal$Signal <- "Signal"
signal <- signal[,c(3,5)]
colnames(signal)<- c("FBgn", "Signal")

write.table(signal, "signal.txt", col.names = T, row.names = F)
```

Evolutionary rate from PAML analysis
```{r}
paml_all <- read.table("paml_mel_yak_ML_update.txt", header=T, sep="\t")
paml_all <- paml_all[,c(3,8:10)]
colnames(paml_all) <- c("FBgn","ML.dN", "ML.dS", "ML.omega")

write.table(paml_all, "paml_all.txt", col.names = T, row.names=F)
```

Covnert with gene names
```{r}
convert <- read.table("FBgn_annotation_ID_fb_2018_06.txt", fill=T, header=T)
convert <- subset(convert, convert$organism_abbreviation == "Dmel")
convert <- convert[,c(3,1)]

write.table(convert, "convert.txt", col.names=T, row.names=F)
```


ModEncode data
```{r}
ME <- read.table("gene_rpkm_report_fb_2018_04.tsv", header=T, sep="\t")
ME <- ME[,c(2,3,5,7,8,11)]

#Data set is formatted annoyingly, easiest thing to do was separate all samples of interest out individually and then put them back together
ME.F <- ME[c(grep('AdF_Ecl_5days', ME$RNASource_name)),]
ME.F <- ME.F[,c(1,5)]
colnames(ME.F) <- c("FBgn", "F")

ME.M <- ME[c(grep('AdM_Ecl_5days', ME$RNASource_name)),]
ME.M <- ME.M[,c(1,5)]
colnames(ME.M) <- c("FBgn", "M")

#Create data table of just log2FC between whole female and whole male
ME.FM <- full_join(ME.F, ME.M, by="FBgn")
ME.FM[is.na(ME.FM)] <- 0
ME.FM$FM <- signif(log(ME.FM$F +1, 2) - log(ME.FM$M +1, 2),3)
ME.FM <- ME.FM[,c(1,4)]

write.table(ME.FM, "sexbias.ME.txt", col.names = T, row.names = F)

#Do the same for all the tissues
ME.testis <-ME[c(grep('testis', ME$RNASource_name)),]
ME.testis <- ME.testis[,c(1,5)]
colnames(ME.testis) <- c("FBgn", "Testis")

ME.ag <- ME[c(grep('acc_gland', ME$RNASource_name)),]
ME.ag <- ME.ag[,c(1,5)]
colnames(ME.ag) <- c("FBgn", "AG")

ME.ovaryV <- ME[c(grep('VirF_4d_ovary', ME$RNASource_name)),]
ME.ovaryV <- ME.ovaryV[,c(1,5)]
colnames(ME.ovaryV) <- c("FBgn", "Ovary.V")

ME.ovaryM <- ME[c(grep('MateF_4d_ovary', ME$RNASource_name)),]
ME.ovaryM <- ME.ovaryM[,c(1,5)]
colnames(ME.ovaryM) <- c("FBgn", "Ovary.M")

ME.headFV <- ME[c(grep('mE_mRNA_A_VirF_4d_head', ME$RNASource_name)),]
ME.headFV <- ME.headFV[,c(1,5)]
colnames(ME.headFV) <- c("FBgn", "Head.F.V")

ME.headFM <- ME[c(grep('mE_mRNA_A_MateF_4d_head', ME$RNASource_name)),]
ME.headFM <- ME.headFM[,c(1,5)]
colnames(ME.headFM) <- c("FBgn", "Head.F.M")

ME.headMM <- ME[c(grep('mE_mRNA_A_MateM_4d_head', ME$RNASource_name)),]
ME.headMM <- ME.headMM[,c(1,5)]
colnames(ME.headMM) <- c("FBgn", "Head.M")

ME.gut <- ME[c(grep('4d_dig_sys', ME$RNASource_name)),]
ME.gut <- ME.gut[,c(1,5)]
colnames(ME.gut) <- c("FBgn", "Gut")

ME.carcass <- ME[c(grep('mE_mRNA_A_4d_carcass', ME$RNASource_name)),]
ME.carcass <- ME.carcass[,c(1,5)]
colnames(ME.carcass) <- c("FBgn", "Carcass")

#create data table of ME tissue data
ME.tissue <- full_join(ME.testis, ME.ag)
ME.tissue <- full_join(ME.tissue, ME.ovaryV)
ME.tissue <- full_join(ME.tissue, ME.ovaryM)
ME.tissue <- full_join(ME.tissue, ME.gut)
ME.tissue <- full_join(ME.tissue, ME.headFV)
ME.tissue <- full_join(ME.tissue, ME.headFM)
ME.tissue <- full_join(ME.tissue, ME.headMM)
ME.tissue <- full_join(ME.tissue, ME.carcass)

# Calculate averages and put together tissue data set
ME.tissue$OvaryAvg <- rowMeans(ME.tissue[,c(4,5)])
ME.tissue$HeadAvg <- rowMeans(ME.tissue[,c(7:8)])
ME.tissue$HeadAvg <- rowMeans(ME.tissue[,c(9,12)])
ME.tissue <- ME.tissue[,c(1,2,3,6,10,11,12)]
ME.tissue[is.na(ME.tissue)] <- 0

#Finalize whole ME dataset with log2RPKM
ME.tissue[,c(2:7)] <- log(ME.tissue[,c(2:7)] + 1, 2)

#determine which tissue has max expression
ME.tissuemax <- ME.tissue
ME.tissuemax$maxME <- apply(ME.tissuemax[,c(2:7)],1, which.max)
ME.tissuemax$tissuemaxME <- with(ME.tissuemax,
ifelse(ME.tissuemax$maxME ==1 & ME.tissuemax$Testis > 0, "Testis",
ifelse(ME.tissuemax$maxME ==2, "AG",
ifelse(ME.tissuemax$maxME ==3, "Gut",
ifelse(ME.tissuemax$maxME ==4, "Carcass",
ifelse(ME.tissuemax$maxME ==5, "Ovary",
ifelse(ME.tissuemax$maxME ==6, "Head", "NoData")))))))

write.table(ME.tissuemax, "ME.tissue.txt", col.names = T, row.names = F)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
